Higgs Assisted Razor Search for Higgsinos at 100 TeV

### 2019-07-23 main.tex
Pushing latest overleaf version

  A 100 TeV proton-proton collider will be an extremely effective way to probe
  the electroweak sector of the Minimal Supersymmetric Standard Model (MSSM).
  In this paper, we describe a search strategy  for discovering pair-produced
  Higgsino-like next-to-lightest supersymmetric particles (NLSP)  at a 100 TeV
  hadron collider that decay to Bino-like lightest supersymmetric particle
  (LSP) via intermediate $Z$ and SM Higgs bosons that in turn decay to a pair
  of leptons and a pair of $b$-quarks respectively: $\N_{2}\N_{3} \rightarrow
  (Z\N_1)(h\N_1)\rightarrow bb\ell\ell+\N_1\N_1$. In addition, we examine the
  potential for machine learning techniques to boost the power of our searches.
  Using this analysis, Higgsinos up to 1.4 TeV can be discovered for Binos with
  masses of about
  0.9 TeV using 3000 fb$^{-1}$ of data. Additionally, Higgsinos up to 1.8
  TeV can be excluded for Binos with masses of about 1.3 TeV at 95\% C.L.   This search
  channel extends the multi-lepton search limits, especially in the region
  where the mass difference between Higgsino NLSP and Bino LSP is smaller.
\Shufang{Update the numbers.} \Adarsh{They are consistent with the text now.}}

\begin{document} 
\maketitle
\flushbottom

@@

 % Why go beyond the MSSM?
Though a natural MSSM spectrum has the potential to tame the hierarchy
problem, it is under siege from recent data from the Large Hadron
Collider (LHC) \cite{Aaboud:2018ujj, Sirunyan:2018vjp}. 
A compelling alternative scenario comes in the form of
split supersymmetry (split SUSY) \cite{Wells:2003tf,
ArkaniHamed:2004yi, Giudice:2004tc}. In this scenario, the lightest
superpartners are the fermionic ones, on the
scale of 1-10 TeV, while the scalar superpartners can be much heavier,
on the scale of 100 - 1000 TeV. In exchange for accepting some level of
fine-tuning, we obtain numerous benefits, including the suppression of
flavor-changing neutral currents and greater compatibility with data
from CP-violation experiments.  The low lying 
fermionic superpartners consist of neutralinos and charginos (collectively
known as electroweakinos), and gluinos. The current LHC search limits on
gluinos are already around 2 TeV for prompt decay and 2.46 TeV for disappearing track searches~\cite{CMS-PAS-SUS-19-005}.   The
limits on electroweakinos with heavy scalar superparticles,
however, are still relatively weak: around 650 $-$ 750 GeV or  less~\cite{ATL-PHYS-PUB-2019-022, Sirunyan:2017lae,Aaboud:2018htj,Sirunyan:2018ubx,Aaboud:2018zeb}, depending on
the decay modes of the parent electroweakinos and their species.  In this paper, we will
focus on the discovery potential of the neutralinos and charginos at the 100
TeV $pp$ collider.

@@

\begin{equation}
\mathbf{M}_{\widetilde{N}}=
\begin{pmatrix}
  M_1 & 0 & -\cb\sw\mz & \sinb\sw\mz \\
  0 & M_2 & \cb\cw\mz & -\sinb\cw\mz \\
  -\cb\sw\mz & \cb\cw\mz & 0 & -\mu \\
  \sinb\sw\mz & -\sinb\cw\mz & -\mu & 0
\end{pmatrix},
\end{equation}
where we employ the notation $s_W, c_W = \sin\theta_W, \cos\theta_W$
for $\theta_W$ being the Weinberg mixing angle. $s_\beta, c_\beta$ are defined
accordingly with $\tan\beta= v_u/v_d$, where $v_u$ and $v_d$ are the vacuum
expectation values of $H_u^0$ and $H_d^0$, with $v_u^2+v_d^2=v^2=(246\ {\rm
GeV})^2$. The parameters $M_1$, $M_2$, and $\mu$ are the mass parameters of
Bino, Wino, and Higgsinos.  The mass eigenstates are usually labels as
$\chi_i^0$ for $i=1 \ldots 4$ with increasing mass eigenvalues.

@@

The optimal search strategy for finding electroweakinos   highly depends on
  their mass spectrums \cite{Han:2013kza}.  Phenomenological collider studies on finding electroweakinos with a small mass splitting of about 0.1 - 50 GeV at a 100 TeV collider can be
found in \cite{Low:2014cba, Bramante:2014tba, Berlin:2015aba, Cirelli:2014dsa},
\Shufang{Say a few words about typical search strategy there.} \Adarsh{I
believe I've already addressed this with the paragraphs I added below in response
to your comment ... let me know if I should add more details.}. \Shufang{What
you said below is for well separated spectra, not for mass spitting of 0.1 to
50 GeV.}
Well-separated spectra have been studied in \cite{Gori:2014oua,
Acharya:2014pua} using
multi-lepton channels, of the form 
\begin{align}
  pp\rightarrow \widetilde{\chi}_i\widetilde{\chi}_j\rightarrow VV +
  \widetilde{\chi}_1^0\widetilde{\chi}_1^0\rightarrow 2\ell/3\ell +  
  \met,
\end{align}
where $\widetilde{\chi}_{i,j}$ can be a neutralino or chargino,
$\widetilde{\chi}_1^0$ is the lightest neutralino, and $V$ being any of the SM gauge bosons $W$, $Z$ or scalar $h$.  These searches work well since
the large mass difference between the electroweakinos can lead to energetic
leptons that can be easily identified. Among the multi-lepton searches for
Higgsinos, the trilepton searches: $\widetilde\chi_{2,3}^0\widetilde\chi_1^\pm\rightarrow WZ\widetilde\chi_1^0\widetilde\chi_1^0\rightarrow \ell\ell\ell + \met$, with $\ell=e, \ \mu$,  have the best reach, due to the relatively high production cross-section of
chargino-neutralino pairs combined with the large reduction in $t\overline{t}$
and QCD backgrounds obtained by requiring three leptons.  Higgsino NLSPs can be excluded at 95\% C.L. with mass up to 2.85 TeV or be discovered with  mass up to 1.8 TeV, for massless Bino LSP.   The reach reduces for larger $M_1$, which vanishes for $M_1\gtrsim 600$ GeV (1000 GeV) for discovery (exclusion).    Multilepton searches
with \emph{Zh} and \emph{ZZ} as the intermediate dibosons are unlikely to be as powerful,
due to the smaller pair-production cross-section of neutral Higgsinos, combined
with the low branching ratio of \emph{Z/h} to leptons. However, if we move beyond
multilepton searches, the channel with \emph{Zh} (originally suggested in
\cite{Han:2013kza}) as the intermediate dibosons emerges as a possible
competitor to the \emph{WZ} channel.

\begin{table}
  \centering
  \begin{tabular}{l|rr}
    \toprule
    Stage & $\N_{2,3}\widetilde{\chi}^\pm_{1}$ & $\N_2\N_3$\\
    \midrule
    Pair production cross section & 60 fb & 16 fb\\
    Intermediate diboson contribution & ($WZ$) 30 fb  & ($Zh$) 8 fb \\
    Applying \emph{BR}$(W\rightarrow \ell\nu)$, \emph{BR}$(Z\rightarrow \ell\ell)$ \& \emph{BR}$(h\rightarrow bb)$ & 0.42 fb & 0.32 fb\\
    \bottomrule
  \end{tabular}
  \caption{Comparison of Higgsino pair production cross-sections for
    $(\widetilde{\chi}_{2,3}^0\widetilde{\chi}^\pm_{1})$ and
    $(\N_{2}\N_{3})$, for $\mu\approx 1$ TeV, at a 100
    TeV \emph{pp} collider. The pair-production cross sections are taken from
    \cite{Gori:2014oua}. The branching ratio to intermediate dibosons is
    evaluated in the limit where the Goldstone equivalence theorem applies, so
    that BR$(\widetilde{\chi}_{2,3}^0\rightarrow Z \widetilde{ \chi}_{1}^0)\approx$
    BR$(\widetilde{\chi}_{2,3}^0\rightarrow h\widetilde{\chi}_1^0)\approx 50\% $ for massless $\widetilde{\chi}_{1}^0)$, 
    and the branching ratios to the SM final states are taken from
    \cite{Olive:2016xmw}.  
    \Shufang{use the actual Br.} \Adarsh{As for the actual BR, I assume you mean
  calculate it using SUSY-HIT? That'll take a bit more time, but I'll try to
  get it.} \Shufang{You can read the number out from right panel of Fig. 2.} }
  \label{tab:xsections}
\end{table}

For pair produced Higgsinos $\widetilde\chi_2^0\widetilde\chi_3^0$ in a scenario with
decoupled Winos and  sfermions, the \emph{Zh} mode has the greatest
branching ratio.  After multiplying all the branching fractions, the signal cross
sections of

\begin{align}
pp\rightarrow \widetilde{\chi}_{2}^{0}\widetilde{\chi}_{3}^{0}\rightarrow
(Z\widetilde{\chi}_1^{0})(h\widetilde{\chi}_1^{0})\rightarrow
bb\ell\ell \chi_1^0\chi_1^0.
\end{align}
become comparable  to trilepton processes, as shown in    table \ref{tab:xsections}.    The signal contains two
\emph{b}-jets, two same flavor, opposite sign leptons, and missing transverse
energy. The main backgrounds for this process are: $t\overline{t}$, \emph{tbW} with
the $b$ and $W$ not coming from a \emph{t}, and \emph{bbWW} with no intermediate
$s$-channel top quarks.

\begin{comment}
\begin{figure}%
  \centering
  \image{0.21}{signal}
  \image{0.21}{tt}
  \image{0.27}{tbW}
  \image{0.27}{bbWW}
  \caption{From left to right, the representative Feynman diagrams of the signal
    process, the dominant \emph{tt} background, \emph{tbW} without a top quark in the
    \emph{s}-channel, and \emph{bbWW} without a top quark in the \emph{s}-channel. (Generated
    using \cite{Ellis:2016jkw}.) \Shufang{Use $\chi_i^0$ etc.}}%
  \label{fig:feynman_diagrams}
\end{figure}
\end{comment}

In the left panel of Fig.~\ref{fig:xsection_plot}, we show the pair-production cross section $\widetilde\chi_2^0\widetilde\chi_3^0$ for the Higgsino-like NLSPs.  The cross section varies between
200 fb to 0.5 fb for Higgsino masses between 500 GeV and 2500 GeV. The right
panel of Fig.~\ref{fig:xsection_plot} shows the decay branching fractions of
$\chi_{2,3}^0\rightarrow Z/h \chi_1^0$, as calculated in SUSY-HIT \cite{Djouadi:2006bz}.
While one of the Higgsinos mostly decays to $Z$, the other
Higgsino mostly decays to $h$.  $Zh+\met$ signal thus provide an alternative
discovery channel for Higgsinos.

\begin{figure}[h]
  \centering
  \includegraphics[width=0.49\textwidth]{images/xsection_plot.pdf}
  \includegraphics[width=0.49\textwidth]{images/br_plot.pdf}
  \caption{Higgsino pair production $\widetilde\chi_2^0\widetilde\chi_3^0$
    cross section (left panel), calculated using
    Prospino2~\cite{Beenakker:1999xh},  and decay decay branching fractions
    (right panel), calculated in SUSY-HIT~\cite{Djouadi:2006bz},  as a function
    of $|\mu|$ for $M_1=25$ GeV. However, it should be noted that the dependence
    on $M_1$ is very weak. \Shufang{How about Br? What's the vcalue of M1
    used? Could you make the two plot same aspect ratios? Using plot
digitizer. Also, for ylabel in left panel, the tilde should not go above 0.
Just above $\chi$.  Is there way to change the xlabel of right panel to be
$\mu$ instead of $|\mu|$?  Need to be consistent with the xlabels.
}\Adarsh{The value of $M_1$ used is 25 GeV for the branching ratio plot as
well. I was able to rerun prospino and susyhit, so I didn't need to run the
plotdigitizer for these plots. I also changed the tildes as you suggested.
I changed the x-axis of both plots to $|\mu|$ for consistency - is that ok?}
}
  \label{fig:xsection_plot}
\end{figure}

Searches for pair produced nearly mass-degenerate Higgsinos  have been
performed at ATLAS and CMS for various decay  topologies
\cite{Aaboud:2018htj,Sirunyan:2018ubx,Aaboud:2018zeb}.  
For neutralino-chargino pair production with $WZ$ and $WH$ topologies, the 95\%
C.L. exclusion limits are about 650 GeV, 490 GeV, and 535 GeV for $WZ$, $WH$
and an equal mixture of $WZ+WH$ topology, with the most stringest limits from
the multi-lepton searches.  For neutralino pair production with $ZZ$, $ZH$ and
$HH$ topologies~\footnote{While such searches assume gravitino LSP with
Higgsino NLSP, the limits are still relevant for our Higgsino NLSP with Bino
LSP scenario.}, the limits are about 650 $-$ 750 GeV via multi-lepton or
multi-$b$ jets searches, depending on the decay branching fractions of Higgsino
NLSP.

@@

\begin{comment}
While the majority of the existing searches for supersymmetry focus on gluino
pair production, there are a number of analyses involving electroweak pair
production of charginos and neutralinos as well, which we will attempt to briefly review here.  Searches
involving multiple leptons and missing energy $(2l/3l +\slashed{E}_T)$ in the
final state are described in
\cite{Aaboud:2018sua,Aaboud:2018jiw, ATLAS:2016uwq,Khachatryan:2014qwa,Chatrchyan:2012pka}, assuming a
wino-like NLSP and a bino-like LSP. The best reach is obtained in the $2/3l$
channel by ATLAS with 36.1 fb$^{-1}$ of data, with NLSP masses up to 600 GeV
excluded for massless LSPs \cite{Aaboud:2018sua}.

% AP: These have intermediate sleptons, so I am omitting them.
%Topologies with one or two hadronically-decaying tau leptons and missing energy
%in the final state have been studied in \cite{ATLAS:2016ety,
%Khachatryan:2016trj}, with the greatest reach obtained by ATLAS in
%\cite{ATLAS:2016ety}, using 13 TeV data - they are able to exclude wino-like
%NLSPs up to a mass of 700 GeV for a massless bino-like LSP.

Searches with a combination of leptons and jets in the final states can be found
in \cite{Aad:2014vma,Khachatryan:2015kxa,Khachatryan:2014mma}. Winos up to 465
GeV are excluded in the $2l + 0/2j$ final states in \cite{Aad:2014vma}. A
compressed mass spectrum is studied in \cite{Khachatryan:2015kxa}, with a mass
difference of about 50 GeV between winos and binos. This study uses the vector
boson fusion channel, with a final state of $2l + 2j + \slashed{E}_T$, and
excludes winos up to a mass of 170 GeV. Of particular interest to us is the
analysis in \cite{Khachatryan:2014mma}, where higgsinos can be excluded up to a
mass of 380 GeV using the $bbll + \slashed{E}_T$ final state, but cannot be
discovered in any region of the relevant parameter space. As we shall see, a 100
TeV collider will enable us to greatly improve upon these limits.
\end{comment}

@@

We simulated parton-level events using \texttt{MadGraph5 v2.3.2.2} and
\texttt{MadEvent} \cite{Alwall:2014hca}, then passed those events to Pythia 6
\cite{Sjostrand:2006za} for showering and hadronization. Finally, we used
\texttt{Delphes 3} \cite{deFavereau:2013fsa} to perform a fast, parametrized
detector simulation, with the detector card devised by the FCC-hh working
group\footnote{\url{https://github.com/HEP-FCC/FCCSW/blob/master/Sim/SimDelphesInterface/data/FCChh_DelphesCard_Baseline_v01.tcl}}.
For the backgrounds, we allowed up to one additional jet in the final state, to
approximate NLO QCD effects, and performed MLM matching with the \texttt{xqcut}
parameter set to 40 GeV. The Higgsino pair production cross sections were
calculated using \texttt{Prospino2}~\cite{Beenakker:1999xh}. \Shufang{tree level or NLO or what?}  To decouple the
Wino, we set its mass parameter $M_2$ to 5 TeV.

Since we expect our signal process to have a dilepton resonance from an on-shell
$Z$ boson, we restricted the phase space for event generation for backgrounds to
the region where the invariant mass of dilepton pairs lies between 80 and 100
GeV. Additionally, the Bino dark matter that escapes the detector would result
in a large amount of missing transverse energy ($\met$), so we required
a minimum $\met$ of 100 GeV at the parton level for the backgrounds as
well. \Shufang{This is only for BG, right?  No such cuts are imposed for
signal generation?} \Adarsh{Yes, the MET cut was only for background.}

@@

  \item \emph{Razor variables}:  Two razor variables are used in our analyses: 
\begin{align}
M_R &= \sqrt{(E_Z+E_h)^2 - (p_Z^z + p_h^z)^2},\\
M_T^R &= \sqrt{\frac{1}{2}\left[\slashed{E}_T(|\vec{p}_{ZT}|+|\vec{p}_{hT}|)
- \vec{\slashed{E}}_T\cdot(\vec{p}_{ZT}+\vec{p}_{hT})\right]}
\end{align}
 for $E_{Z,h}$ and $\vec{p}_{Z,h}$ being the reconstructed energy and momentum for $Z$ and $h$, respectively.
      Representative kinematic
  distributions of these variables for signal events of a 1 TeV Higgsino and a 25 GeV Bino, as well as $tt$ and $tbW$ backgrounds are
  shown in Fig.~\ref{fig:razor_histos}, after the trigger, identification,
  $m_{\ell^+\ell^-}$, and
  $\slashed{E}_{T}$ cuts.  \Shufang{How about mll cut? BG is generated with mll
  cut.}  \Adarsh{I have added the $m_{ll}$ cut to the sentence.} The
  distribution for the \emph{bbWW} background is not shown, since it is negligible in
  comparison to the others.   We can see that the distribution of $M_R$ is peaked
  around 1 TeV for the signal, which is consistent with what we would expect as   it corresponds to the mass difference between the NLSP and LSP.  The $tt$ background peaks around 500 GeV, while the distribution of $tbW$ background almost overlaps with that of the signal process.  Similar behaviour also appears for $M_T^R$ distributions.  
  For this mass combination, requiring $M_R >$ 800
  GeV and $M_T^R >$ 400 GeV yields the greatest significance.

@@

\begin{figure}[h]
\centering
\includegraphics[trim = {0.3cm 0.6cm 0.1cm 0}, clip, width=0.496\textwidth]{images/mR_copy.png}
\includegraphics[trim = {0.3cm 0.6cm 0.1cm 0}, clip, width=0.496\textwidth]{images/mTR_copy.png}
\caption{Normalized distributions of the razor kinematical variables $M_R$
  (left) and $M_T^R$ (right) for signal process with a 1 TeV Higgsino NLSP and 25 GeV Bino LSP,  as well as the dominant $tt$ and $tbW$ backgrounds,
  after the trigger, identification, and $\slashed{E}_{T}$ cuts.}
\label{fig:razor_histos}
\end{figure}

\begin{table}[h]
  \centering
  \input{tables/cutflowtable.tex}
  \caption{Representative cut flow table for the benchmark point $\mu=1$ TeV,
    $M_1 = 25$ GeV at 100  TeV $pp$ collider, for a traditional cut-and-count analysis. All cross sections
    are given in unit of fb, and the units for the missing energy, invariant
    mass, and razor variable cuts are GeV. The significance, $S/\sqrt{B}$, is
    calculated for an integrated luminosity of 3 ab$^{-1}$. \Shufang{MET $>$
  400 or $<$ 400? } \Adarsh{$> 400$ - I've fixed it now.}}
\label{tab:cc_cutflowtable}
\end{table}

>>>>

  A 100 TeV proton-proton collider will be an extremely effective way to probe
  the electroweak sector of the Minimal Supersymmetric Standard Model (MSSM).
  In this paper, we describe a search strategy  for discovering pair-produced
  Higgsino-like next-to-lightest supersymmetric particles (NLSP)  at a 100 TeV
  hadron collider that decay to Bino-like lightest supersymmetric particle
  (LSP) via intermediate $Z$ and SM Higgs bosons that in turn decay to a pair
  of leptons and a pair of $b$-quarks respectively: $\N_{2}\N_{3} \rightarrow
  (Z\N_1)(h\N_1)\rightarrow bb\ell\ell+\N_1\N_1$. In addition, we examine the
  potential for machine learning techniques to boost the power of our searches.
  Using this analysis, Higgsinos up to 1.4 TeV can be discovered for Binos with
  masses of about
  0.9 TeV using 3000 fb$^{-1}$ of data. Additionally, Higgsinos up to 1.8
  TeV can be excluded for Binos with masses of about 1.4 TeV at 95\% C.L.   This search
  channel extends the multi-lepton search limits, especially in the region
  where the mass difference between Higgsino NLSP and Bino LSP is smaller.
 }

\begin{document} 
\maketitle
%\flushbottom

@@

 % Why go beyond the MSSM?
Though a natural MSSM spectrum has the potential to tame the hierarchy
problem, it is under siege from recent data from the Large Hadron
Collider (LHC) \cite{Aaboud:2018ujj, Sirunyan:2018vjp}. 
A compelling alternative scenario comes in the form of
split supersymmetry (split SUSY) \cite{Wells:2003tf,
ArkaniHamed:2004yi, Giudice:2004tc}. In this scenario, the lightest
superpartners are the fermionic ones, on the
scale of 1-10 TeV, while the scalar superpartners can be much heavier,
on the scale of 100 - 1000 TeV. In exchange for accepting some level of
fine-tuning, we obtain numerous benefits, including the suppression of
flavor-changing neutral currents and greater compatibility with data
from CP-violation experiments.  The low lying 
fermionic superpartners consist of neutralinos and charginos (collectively
known as electroweakinos), and gluinos. The current LHC search limits on
gluinos are already around 2 TeV for prompt decay and 2.5 TeV for disappearing track searches~\cite{CMS-PAS-SUS-19-005}.   The
limits on electroweakinos with heavy scalar superparticles,
however, are still relatively weak: around 650 $-$ 750 GeV or  less~\cite{ATL-PHYS-PUB-2019-022, Sirunyan:2017lae,Aaboud:2018htj,Sirunyan:2018ubx,Aaboud:2018zeb}, depending on
the decay modes of the parent electroweakinos and their species.  In this paper, we will
focus on the discovery potential of the neutralinos and charginos at the 100
TeV $pp$ collider.

@@

\begin{equation}
\mathbf{M}_{\widetilde{N}}=
\begin{pmatrix}
  M_1 & 0 & -\cb\sw\mz & \sinb\sw\mz \\
  0 & M_2 & \cb\cw\mz & -\sinb\cw\mz \\
  -\cb\sw\mz & \cb\cw\mz & 0 & -\mu \\
  \sinb\sw\mz & -\sinb\cw\mz & -\mu & 0
\end{pmatrix},
\end{equation}
where we employ the notation $s_W, c_W = \sin\theta_W, \cos\theta_W$
for $\theta_W$ being the Weinberg mixing angle. $s_\beta, c_\beta$ are defined
accordingly with $\tan\beta= v_u/v_d$, where $v_u$ and $v_d$ are the vacuum
expectation values of $H_u^0$ and $H_d^0$, with $v_u^2+v_d^2=v^2=(246\ {\rm
GeV})^2$. The parameters $M_1$, $M_2$, and $\mu$ are the mass parameters of
Bino, Wino, and Higgsinos.  The mass eigenstates are usually labeled as
$\chi_i^0$ for $i=1 \ldots 4$ with increasing mass eigenvalues.

@@

The optimal search strategy for finding electroweakinos   highly depends on
  their mass spectra \cite{Han:2013kza}.  Phenomenological collider studies on finding electroweakinos with a small mass splitting of about 0.1 - 50 GeV at a 100 TeV collider can be
found in \cite{Low:2014cba, Bramante:2014tba, Berlin:2015aba, Cirelli:2014dsa},
\Shufang{Say a few words about typical search strategy there.}
\Adarsh{Yes, I focused more on well separated spectra since that is more similar to our case - should I add more details for the 0.1 - 50 GeV compressed spectra studies?} \Shufang{Add a couple sentences here of the search strategy for the small mass splitting case.}
Well-separated spectra have been studied in \cite{Gori:2014oua,
Acharya:2014pua} using
multi-lepton channels, of the form 
\begin{align}
  pp\rightarrow \widetilde{\chi}_i\widetilde{\chi}_j\rightarrow VV +
  \widetilde{\chi}_1^0\widetilde{\chi}_1^0\rightarrow 2\ell/3\ell +  
  \met,
\end{align}
where $\widetilde{\chi}_{i,j}$ can be a neutralino or chargino,
$\widetilde{\chi}_1^0$ is the lightest neutralino, and $V$ being any of the SM gauge bosons $W$, $Z$ or scalar $h$.  These searches work well since
the large mass difference between the electroweakinos can lead to energetic
leptons that can be easily identified. Among the multi-lepton searches for
Higgsinos, the trilepton searches: $\widetilde\chi_{2,3}^0\widetilde\chi_1^\pm\rightarrow WZ\widetilde\chi_1^0\widetilde\chi_1^0\rightarrow \ell\ell\ell + \met$, with $\ell=e, \ \mu$,  have the best reach, due to the relatively high production cross-section of
chargino-neutralino pairs combined with the large reduction in $t\overline{t}$
and QCD backgrounds obtained by requiring three leptons.  Higgsino NLSPs can be excluded at 95\% C.L. with mass up to 2.8 TeV or be discovered with  mass up to 1.8 TeV, for a massless Bino LSP.   The reach reduces for larger $M_1$, which vanishes for $M_1\gtrsim 600$ GeV (1000 GeV) for discovery (exclusion).    Multilepton searches
with \emph{Zh} and \emph{ZZ} as the intermediate dibosons are unlikely to be as powerful,
due to the smaller pair-production cross-section of neutral Higgsinos, combined
with the low branching ratio of \emph{Z/h} to leptons. However, if we move beyond
multilepton searches, the channel with \emph{Zh} (originally suggested in
\cite{Han:2013kza}) as the intermediate dibosons emerges as a possible
competitor to the \emph{WZ} channel.

In the left panel of Fig.~\ref{fig:xsection_plot}, we show the pair-production cross section $\widetilde\chi_2^0\widetilde\chi_3^0$ for the Higgsino-like NLSPs.  The cross section varies between
200 fb to 0.5 fb for Higgsino masses between 500 GeV and 2500 GeV. The right
panel of Fig.~\ref{fig:xsection_plot} shows the decay branching fractions of
$\chi_{2,3}^0\rightarrow Z/h \chi_1^0$, as calculated in SUSY-HIT \cite{Djouadi:2006bz}.
While one of the Higgsinos mostly decays to $Z$, the other
Higgsino mostly decays to $h$.    Therefore,  for pair produced Higgsinos $\widetilde\chi_2^0\widetilde\chi_3^0$, the \emph{Zh} mode has the greatest
branching fraction.  After multiplying all the branching fractions, the signal cross sections of 
\begin{align}
pp\rightarrow \widetilde{\chi}_{2}^{0}\widetilde{\chi}_{3}^{0}\rightarrow
(Z\widetilde{\chi}_1^{0})(h\widetilde{\chi}_1^{0})\rightarrow
bb\ell\ell \chi_1^0\chi_1^0.
\end{align}
become comparable  to trilepton processes, as shown in    table \ref{tab:xsections}.   $Zh+\met$ signal thus provide an alternative
discovery channel for Higgsinos.   The signal contains two
\emph{b}-jets, two same flavor, opposite sign leptons, and missing transverse
energy. The main backgrounds for this process are: $t\overline{t}$, \emph{tbW} with
the $b$ and $W$ not coming from a \emph{t}, and \emph{bbWW} with no intermediate
$s$-channel top quarks.

\begin{figure}[h]
  \centering
  \includegraphics[width=0.49\textwidth]{images/xsection_plot.pdf}
  \includegraphics[width=0.49\textwidth]{images/br_plot.pdf}
  \caption{Higgsino pair production $\widetilde\chi_2^0\widetilde\chi_3^0$
    cross section (left panel), calculated using
    Prospino2~\cite{Beenakker:1999xh},  and decay branching fractions
    (right panel), calculated in SUSY-HIT~\cite{Djouadi:2006bz},  as a function
    of $\mu$ for $M_1=25$ GeV. However, it should be noted that the dependence
    on $M_1$ is very weak.  \Shufang{Could you use $\mu$ for both xlabels?  The CS and Br will depend slightly on the sign of mu.  Since we do use positive mu in our analyses, let's label it this way.  I have a footnote in intro to explain the sign effect of mu.  Also, change right panel, ylabel to be either Br or Branching Fraction.}
}
  \label{fig:xsection_plot}
\end{figure}

\begin{table}
  \centering
  \begin{tabular}{l|rr}
    \toprule
    Stage & $\N_{2,3}\widetilde{\chi}^\pm_{1}$ & $\N_2\N_3$\\
    \midrule
    Pair production cross section & 60 fb & 17.2 fb\\
    Intermediate diboson contribution & ($WZ$) 29.7 fb  & ($Zh$) 9.15 fb \\
    Applying \emph{BR}$(W\rightarrow \ell\nu)$, \emph{BR}$(Z\rightarrow \ell\ell)$ \& \emph{BR}$(h\rightarrow bb)$ & 0.42 fb & 0.37 fb\\
    \bottomrule
  \end{tabular}
  \caption{Comparison of Higgsino pair production cross-sections for
    $(\widetilde{\chi}_{2,3}^0\widetilde{\chi}^\pm_{1})$ and
    $(\N_{2}\N_{3})$, for $\mu\approx 1$ TeV, at a 100
    TeV \emph{pp} collider. 
    The pair-production cross section for $\N_{2,3}\widetilde{\chi}^\pm_1$ is taken from
    \cite{Gori:2014oua}, while the pair-production cross-section for $\N_2\N_3$ is calculated at Next-to-Leading Order (NLO) using Prospino2. The branching ratios to the diboson intermediate states are calculated using SUSY-HIT, and the branching ratios to the SM final states are taken from
    \cite{Olive:2016xmw}.    }
  \label{tab:xsections}
\end{table}

Searches for pair produced nearly mass-degenerate Higgsinos  have been
performed at ATLAS and CMS for various decay  topologies
\cite{Aaboud:2018htj,Sirunyan:2018ubx,Aaboud:2018zeb}.  
For neutralino-chargino pair production with $WZ$ and $WH$ topologies, the 95\%
C.L. exclusion limits are about 650 GeV, 490 GeV, and 535 GeV for $WZ$, $WH$
and an equal mixture of $WZ+WH$ topology, with the most strongest limits from
the multi-lepton searches.  For neutralino pair production with $ZZ$, $ZH$ and
$HH$ topologies~\footnote{While such searches assume gravitino LSP with
Higgsino NLSP, the limits are still relevant for our Higgsino NLSP with Bino
LSP scenario.}, the limits are about 650 $-$ 750 GeV via multi-lepton or
multi-$b$ jets searches, depending on the decay branching fractions of Higgsino
NLSP.

@@

@@

We simulated parton-level events using \texttt{MadGraph5 v2.3.2.2} and
\texttt{MadEvent} \cite{Alwall:2014hca}, then passed those events to Pythia 6
\cite{Sjostrand:2006za} for showering and hadronization. Finally, we used
\texttt{Delphes 3} \cite{deFavereau:2013fsa} to perform a fast, parametrized
detector simulation, with the detector card devised by the FCC-hh working
group\footnote{\url{https://github.com/HEP-FCC/FCCSW/blob/master/Sim/SimDelphesInterface/data/FCChh_DelphesCard_Baseline_v01.tcl}}.
For the backgrounds, we allowed up to one additional jet in the final state, to
approximate NLO QCD effects, and performed MLM matching with the \texttt{xqcut}
parameter set to 40 GeV. The Higgsino pair production cross sections were
calculated using \texttt{Prospino2}~\cite{Beenakker:1999xh} at NLO.  
To decouple the Wino, we set its mass parameter $M_2$ to 3 TeV.

Since we expect our signal process to have a dilepton resonance from an on-shell
$Z$ boson, we restricted the phase space for event generation for backgrounds to
the region where the invariant mass of dilepton pairs lies between 80 and 100
GeV. Additionally, the Bino dark matter that escapes the detector would result
in a large amount of missing transverse energy ($\met$), so we required
a minimum $\met$ of 100 GeV at the parton level for the backgrounds as
well.

@@

  \item \emph{Razor variables}:  Two razor variables are used in our analyses: 
\begin{align}
M_R &= \sqrt{(E_Z+E_h)^2 - (p_Z^z + p_h^z)^2},\\
M_T^R &= \sqrt{\frac{1}{2}\left[\slashed{E}_T(|\vec{p}_{ZT}|+|\vec{p}_{hT}|)
- \vec{\slashed{E}}_T\cdot(\vec{p}_{ZT}+\vec{p}_{hT})\right]}
\end{align}
 for $E_{Z,h}$ and $\vec{p}_{Z,h}$ being the reconstructed energy and momentum for $Z$ and $h$, respectively.
      Representative kinematic
  distributions of these variables for signal events of $\mu=1$ TeV Higgsinos NLSP and a $M_1=25$ GeV Bino LSP, as well as $tt$ and $tbW$ backgrounds are
  shown in Fig.~\ref{fig:razor_histos}, after the trigger, identification,
  $\slashed{E}_{T}$,  and  $m_{\ell^+\ell^-}$cuts.   \Shufang{BG generator level mll and MET cut (MET bigger tan 100 GeV), or cut level mll and MET cut (MET bigger than 400 GEV)? Both signal and backgrounds?} The
  distribution for the \emph{bbWW} background is not shown, since it is negligible in
  comparison to the others.   We can see that the distribution of $M_R$ is peaked
  around 1 TeV for the signal, which is consistent with what we would expect as   it corresponds to the mass difference between the NLSP and LSP.  The $tt$ background peaks around 500 GeV, while the distribution of $tbW$ background almost overlaps with that of the signal process.  Similar behaviour also appears for $M_T^R$ distributions.  
  For this mass combination, requiring $M_R >$ 800
  GeV and $M_T^R >$ 400 GeV yields the greatest significance.

@@

\begin{figure}[h]
\centering
\includegraphics[trim = {0.3cm 0.6cm 0.1cm 0}, clip, width=0.496\textwidth]{images/mR_copy.png}
\includegraphics[trim = {0.3cm 0.6cm 0.1cm 0}, clip, width=0.496\textwidth]{images/mTR_copy.png}
\caption{Normalized distributions of the razor kinematic variables $M_R$
  (left) and $M_T^R$ (right) for signal process with $\mu=1$ TeV Higgsinos NLSP and a $M_1=25$ GeV Bino LSP,  as well as the dominant $tt$ and $tbW$ backgrounds,
  after the trigger, identification,  $\slashed{E}_{T}$ and $m_{\ell^+\ell^-}$ cuts.}
\label{fig:razor_histos}
\end{figure}

\begin{table}[h]
  \centering
  \input{tables/cutflowtable.tex}
  \caption{Representative cut flow table for the benchmark point $\mu=1$ TeV,
    $M_1 = 25$ GeV at 100  TeV $pp$ collider, for a traditional cut-and-count analysis. All cross sections
    are given in unit of fb, and the units for the missing energy, invariant
    mass, and razor variable cuts are GeV. The significance, $S/\sqrt{B}$, is
    calculated for an integrated luminosity of 3 ab$^{-1}$.  }
\label{tab:cc_cutflowtable}
\end{table}

Table \ref{tab:cc_cutflowtable} shows the cut efficiencies for a representative
signal benchmark point with a $\mu =$ 1 TeV and $M_1$ = 25 GeV.   The
cross-sections of the backgrounds are obtained from MadEvent after performing the MLM matching procedure. Their small size reflects
the $m_{\ell\ell}$ and $\slashed{E}_T$ cuts we imposed at the parton level. For all
the benchmark points, we require a minimum of 3 signal events left over after
cuts. We can see that, after applying our cuts, $tbW$ remains as the
dominant backgrounds, followed by $tt$.   The values of the razor variable cuts were chosen to
maximize the significance, $S/\sqrt{B}$ (calculated for an integrated luminosity
of 3000 fb$^{-1}$), shown in the last column.
